%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Freelance} % Organization
    {Taipei, Taiwan} % Location
    {Apr. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Devoted to open-source software development with 200+ GitHub stars. Subtitle-Downloader achieved 1st-page Google results, 1k+ views, and 100+ clones, demonstrating widespread daily use.}
        \item {Aid small business startups in establishing online stores and supporting them in optimizing their websites for improved SEO.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Business Lecturer} % Job title
  {Taipei Beitou Health Management Hospital} % Organization
  {Taipei, Taiwan} % Location
  {Jun. 2021 - Jul. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led iOS and web application training, emphasizing Swift for e-bulletin boards. Utilized Swift to enhance intranet communication with iOS-based announcement platforms. Implemented Firebase for dynamic push notifications, resulting in a 20\% increase in hospital staff engagement and responsiveness and contributing significantly to the overall organizational communication strategy.}
      \item {Focused on hands-on experience designing medical systems, API development, and database operations. Implemented dynamic push notifications through Firebase for enhanced engagement.}
      \item {Cultivated a problem-solving mindset among colleagues to leverage online applications for efficient work solutions, generating a 25\% reduction in troubleshooting time and boosting workflow efficiency and team productivity.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {E.SUN BANK} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cooperated with IBM to lead the establishment and maintenance of a large-scale online banking system, serving millions of users and ensuring secure financial transactions.}
        \item {Incorporated PayPal API, improving payment processing speed by 20\%. Created a Node.js-based API auto-conversion program that automated field validation for 100+ APIs, shortening completion time from 3 months to 1 month.}
        \item {Designed and executed a modern Content Management System (CMS) for Web-ATM using Angular 6 and Spring Boot. Introduced Continuous Integration/Continuous Deployment practices that significantly enhanced operational efficiency; the system drastically cut report generation time from half a day to 0.5 seconds.}
        \item {Standardized CMS development by converting components into a shared library, speeding up the deployment of forex trading platforms by 6 months. This strategy streamlined processes and cut time-to-market by 15\%, boosting the bank's competitiveness in the fast-paced financial sector.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {School Ambassador, Software Engineer} % Job title
    {College Bike} % Organization
    {Taipei, Taiwan} % Location
    {Apr. 2016 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conceptualized and executed marketing programs, encompassing exhibitions and test rides, to enhance brand visibility.}
        \item {Collaborated on creating a Content Management System using PHP for an e-commerce platform, delivering a 30\% improvement in website performance.}
        \item {Optimized the transaction process to ensure completing each order seamlessly within a timeframe of less than 30 seconds.}
        \item {Implemented WordPress optimizations that led to a 50\% increase in SEO ranking, achieving first-page visibility for targeted keywords without reliance on paid advertisements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {National Taiwan University Hospital, Emergency Medicine Dep.} % Organization
    {Taipei, Taiwan} % Location
    {Oct. 2014 - Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Android applications featuring material design principles specifically tailored for the seamless uploading of medical images.}
        \item {Implemented low-level caching on the server, resulting in a 40\% improvement in service performance and a 25\% reduction in database burden.}
        \item {Spearheaded the development of a medical image teaching platform aligned with the Responsive Web Design model, ensuring seamless usability for doctors across tablets, mobile phones, and computers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {National Cheng Kung University} % Organization
    {Tainan, Taiwan} % Location
    {Jan. 2014 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented an e-learning platform to facilitate nanotechnology education in Taiwan.}
        \item {Transitioned Flash animation to HTML5 format and embraced responsive web design principles, resulting in a 20\% reduction in page loading time and a 5\% rise in visitor dwell time.}
        \item {Developed the comprehensive web application logic and constructed an API server for community service.}
        \item {Applied SEO best practices to enhance website load times, leading to a 20\% increase in website visits.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
