%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant, Volunteer} % Affiliation/role
    {VGHTPE (Taipei Veterans General Hospital)} % Organization/group
    {Taipei, Taiwan} % Location
    {Jun. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Technical Troubleshooting: Proactively identified and resolved computer issues for healthcare professionals, ensuring minimal downtime and optimizing workflow efficiency.}
        \item {Patient Data Management: Spearheaded the organization and management of patient data, contributing to enhanced accuracy and accessibility. Implemented efficient data storage practices to streamline retrieval and analysis processes.}
        \item {Adaptability: Successfully navigated the dynamic healthcare environment, staying abreast of the latest technological advancements and incorporating them into the hospital's IT infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Volunteer} % Affiliation/role
    {NCKU (National Cheng Kung University)} % Organization/group
    {Tainan, Taiwan} % Location
    {Feb. 2015 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Admission Procedures Assistance: Provided personalized guidance to international students, streamlining admission procedures and ensuring a seamless transition into the academic environment. Addressed inquiries and facilitated documentation, fostering a supportive onboarding experience.}
        \item {Language Support: Offered language support to non-native English speakers, facilitating improved communication and integration into academic and social aspects of university life.}
        \item {Event Coordination: Planned and participated in events promoting diversity and cultural exchange. Contributed to the organization and execution of workshops, seminars, and cultural festivals, enriching the university community experience.}
        \item {Cultural Exploration: Orchestrated cultural exchange activities, including cultural events, city tours, and language exchange programs. Facilitated immersive experiences in Taiwanese culture, fostering a rich and inclusive university environment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
